Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-16 paper/tex/appendix.tex
remove superfluous comments from tex

\section{Evaluation of the redshift distribution}
\label{sec:moments}
%(Alex Malz)

@@

%is the most widely accepted method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$.  This procedure is not formally correct, basic statistics tells us that joint probabilities are not formed by adding probabilities.  \citet{Malz:chippr} shows how the stacking procedure can lead to bias in redshift estimates, and develop a principled alternative to this commonly employed method.  However, while  the use of the stacked estimator of the redshift distribution is not formally correct, we use it under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/NZsumplot_12codes_scottsrule.jpg}
\caption{The smoothed stacked estimator $\hat{N}(z)$ of the redshift distribution (red) produced by each code (panels) compared to the true redshift distribution $\tilde{N}(z)$ (blue).
Varying levels of agreement are seen among the codes, with the smallest deviations for \cmnn, \flexzboost, \tpz, and \trainz.}
\label{fig:nz}
%\aim{Arguably this could also be clarified by showing the true $n'(z)$ once and then differences from it for each cod's stacked estimator\dots}\scc{what if we plot the difference between true and stacked rather than soverposing the two lines? Sam please do not hate me.}
\end{figure*}

@@

%\begin{table}
%\setlength{\tabcolsep}{2pt}
%\caption{Moments of the stacked estimator $\hat{N}(z)$ of the redshift distribution.
%Most of the codes considered recover the moments of $\tilde{N}(z)$}
%\label{tab:moments}
%\begin{tabular}{lccc}
%\hline
%\hline
% \multicolumn{4}{l}{Moments of $\hat{N}(z)$} \\
%\hline
%Estimator  & mean       & variance    & skewness \\
%Empirical ``truth'' & 0.701 & 0.630 & 0.671  \\
%\hline
%\annz       & 0.702      & 0.625      & 0.653    \\
%\bpz        & 0.699      & 0.629      & 0.671    \\
%\delight    & 0.692      & 0.609      & 0.638    \\
%\eazy       & 0.681      & 0.595      & 0.619    \\
%\flexzboost & 0.694      & 0.610      & 0.631    \\
%\gpz        & 0.696      & 0.615      & 0.639    \\
%\lephare    & 0.718      & 0.668      & 0.741    \\
%\metaphor   & 0.705      & 0.628      & 0.657    \\
%\cmnn       & 0.701      & 0.628      & 0.667    \\
%\skynet     & 0.743      & 0.708      & 0.797    \\
%\tpz        & 0.700      & 0.619      & 0.643    \\
%\hline
%\trainz	    & 0.699 		 & 0.627 	    & 0.666 \\
%\end{tabular}
%\end{table}

@@

For reference, Section 3.8 of the \lsst\ Science Book \citep{Abell:09} uses the standard definitions of these parameters in requiring
\begin{itemize}
\item RMS scatter $\sigma < 0.02 (1 + z_{\mathrm{true}})$
%\scc{actually the SB reports in page 75 that the goal of 0.02 is for the RMS of $\frac{\sigma_{z}}{(1+z)}$ while we are using IQR}
\item bias $b_{z} < 0.003$ %\scc{in page 518 of the SB is clearly reported that the mean is expected to be less than 0.003 in our case we have defined as bias the median and not the mean }
\item catastrophic outlier rate $f_{\mathrm{out}} < 10$ per cent %\scc{clearly the number of outliers since are defined above $3\sigma$ strictly depends on the sigma definition, in the science book it seems to refer to the RMS of the $e_z$ distribution even ef it could be the standard deviation, but again I don't think it refers to IQR, therefore we could not consider exactly this numbers as reference.}
%\red{I am going off of conversations with Zeljko and how we {\it actually} computed the metrics in the Science Book (I have the scripts).  You are correct that several of these are slightly different than actually stated in the Science Book, or where the Science Book does not use very precise language as to what was done to compute the RMS or define the bias.  We can also cut out those specifics, or maybe say Ivezic private communication, maybe?  Also $\sigma_{z}$ defined in terms of IQR is exactly equivalent to the standard deviation when scaled by 1.349 for a Gaussian distribution, so the numbers are appropriate to cite in this context.  IQR is just a more robust way of calculating sigma for a distribution with outliers.--SJS }
%\scc{I am very sorry I am not saying that IQR is not fine, I want to keep the IQR my concerns are related to the notation and the \textit{reader understanding}, if I wrote $\sigma$ somewhere in a table the reader will understand for sure that is the traditional standard deviation (a lot of people skips the indicators definition for the \textit{obvious} ones), I am suggesting to replace the notation $\sigma$ with the notation $\sigma_{IQR}$ (or something like this) to avoid any confusion, and also to change from $bias$ to $median$ for the same reason. I agree that say Ivezic private communication could be better.}
.
\end{itemize}

@@

The finite grid spacing of the \pzpdf s induces some discretization in $z_{PEAK}$.
%, particularly for \skynet.
The features perpendicular to the $z_{phot} = z_{spec}$ line are due to the $4000$ \AA\ break passing through the gaps between adjacent filters.
% and logically are more prominent for template-based codes
Even the strongest codes feature populations far from the $z_{phot} = z_{spec}$ line representing a degeneracy in the space of colours and redshifts.
% While use of the full information available via $p(z)$ mitigates their impact, a full understanding of the outlier population is critical for LSST science, particularly in tomographic applications.
%\red{I forget what exactly I was trying to say here, if someone else wants to take a crack at this it might be helpful --SJS}
%\scc{may be worth to say that the usage of further bands could mitigate this effect by removing the degeneration  usually induced from emission lines moving across different filters?}

@@

The intrinsic scatter, bias, and catastrophic outlier rate are given in Table~\ref{tab:pointestimates}.
Perhaps unsurprisingly, performance under these metrics largely tracks that of the metrics of Section~\ref{sec:metrics} of the \pzpdf s from which the point estimates were derived.
All twelve codes perform at or near the goals of the \lsst\ Science Requirements Document\footnote{available at: \url{http://ls.st/srd}} and \citet{Graham:17}, which is encouraging if not unexpected for $i < 25.3$.
% But, it is still an encouraging sign, given an updated mock galaxy simulation and the expanded set of photo-$z$ codes tested.
%\red{maybe say consistent with expectations, and a reference to Melissa's paper in here?  What else to say about nearly meeting point goals?}

>>>>

\section{Evaluation of the redshift distribution}
\label{sec:moments}

@@

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/NZsumplot_12codes_scottsrule.jpg}
\caption{The smoothed stacked estimator $\hat{N}(z)$ of the redshift distribution (red) produced by each code (panels) compared to the true redshift distribution $\tilde{N}(z)$ (blue).
Varying levels of agreement are seen among the codes, with the smallest deviations for \cmnn, \flexzboost, \tpz, and \trainz.}
\label{fig:nz}
\end{figure*}

@@

@@

For reference, Section 3.8 of the \lsst\ Science Book \citep{Abell:09} uses the standard definitions of these parameters in requiring
\begin{itemize}
\item RMS scatter $\sigma < 0.02 (1 + z_{\mathrm{true}})$
\item bias $b_{z} < 0.003$ 
\item catastrophic outlier rate $f_{\mathrm{out}} < 10$ per cent 
\end{itemize}

@@

The finite grid spacing of the \pzpdf s induces some discretization in $z_{PEAK}$.
The features perpendicular to the $z_{phot} = z_{spec}$ line are due to the $4000$ \AA\ break passing through the gaps between adjacent filters.
Even the strongest codes feature populations far from the $z_{phot} = z_{spec}$ line representing a degeneracy in the space of colours and redshifts.

@@

The intrinsic scatter, bias, and catastrophic outlier rate are given in Table~\ref{tab:pointestimates}.
Perhaps unsurprisingly, performance under these metrics largely tracks that of the metrics of Section~\ref{sec:metrics} of the \pzpdf s from which the point estimates were derived.
All twelve codes perform at or near the goals of the \lsst\ Science Requirements Document\footnote{available at: \url{http://ls.st/srd}} and \citet{Graham:17}, which is encouraging if not unexpected for $i < 25.3$.
